Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2017-11-15 CVPR16/Source/abstract.tex
Fit into the phdpropoal single column format.

\begin{abstract}
We present a physically interpretable, continuous three-dimensional (3D) model for handling occlusions with applications to road scene understanding. We probabilistically assign each point in space to an object with a theoretical modeling of the reflection and transmission probabilities for the corresponding camera ray. Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion (SFM) point tracks with potentially occluding objects or modeling object detection scores in applications such as 3D localization. For point track association, our model uniformly handles static and dynamic objects, which is an advantage over motion segmentation approaches traditionally used in multibody SFM. Detailed experiments on the KITTI raw dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions. We also demonstrate how our continuous occlusion model may be applied to the task of 3D localization in road scenes.

%This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for modeling objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
\end{abstract}

>>>>

%\begin{abstract}
\section{Abstract}
We present a physically interpretable, continuous three-dimensional (3D) model for handling occlusions with applications to road scene understanding. We probabilistically assign each point in space to an object with a theoretical modeling of the reflection and transmission probabilities for the corresponding camera ray. Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion (SFM) point tracks with potentially occluding objects or modeling object detection scores in applications such as 3D localization. For point track association, our model uniformly handles static and dynamic objects, which is an advantage over motion segmentation approaches traditionally used in multibody SFM. Detailed experiments on the KITTI raw dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions. We also demonstrate how our continuous occlusion model may be applied to the task of 3D localization in road scenes.

%This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for modeling objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
%\end{abstract}

### 2017-11-15 CVPR16/Source/applications.tex
Fit into the phdpropoal single column format.

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{table}[!!t]
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{table}

@@

@@

\begin{figure}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables. (Bottom) The graphical model corresponding to the above frame. In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{figure}

@@

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{multline}
where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

>>>>

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{wraptable}[16]{r}{0.5\textwidth}
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{wraptable}

@@

\begin{wrapfigure}[22]{r}{0.5\textwidth}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables. (Bottom) The graphical model corresponding to the above frame. In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{wrapfigure}

@@

@@

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{align}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  %\\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{align}
where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

### 2017-11-15 CVPR16/Source/occlusion.tex
Fit into the phdpropoal single column format.

\begin{figure}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}\\
  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.9\columnwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
  \vspace{-0.3cm}
  \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$. The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
  \label{fig:compare:exact:approx:ptrans}
  \vspace{-0.3cm}
\end{figure}

>>>>

\begin{wrapfigure}[15]{r}{0.5\textwidth}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{wrapfigure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_pt_vis-small.png}%\\
  \includegraphics[trim=0.0 0 0.3in 0, clip, width=0.45\textwidth]{results/plotPtransmission_exact_vs_approx_embedded_fonts.pdf}
  \vspace{-0.3cm}
  \caption{\small Comparisons between the approximate and exact formulations of $\Ptrans$. The drop in the approximate version is delayed because we assume drop at the object center rather than the camera-facing face of the object.}
  \label{fig:compare:exact:approx:ptrans}
  \vspace{-0.3cm}
\end{figure}
